---
title: "Assigment 1"
author: "Muammer"
format: html
---


## Chapter 1

I choose the video with - Mustafa Baydoğan.

#
Mustafa Baydoğan gave a talk on the interaction between data science and industrial engineering. In his talk, he emphasized how industrial engineers' skills in mathematical modeling and system understanding provide a great advantage in solving data science problems. He also explained in detail how real-world problems can be approached from this perspective, providing examples from various industries.


###  Questions
-   Why is interpretability important for industrial applications?

A) To provide greater accuracy

B) To explain decisions to managers or comply with regulations

C) Reduce computational complexity

D) To implement deep learning techniques

Answer: B

-   Real-world data can often be incomplete, noisy or unorganized. What strategies do you follow when working with this kind of data?

Answer: 
Because real-world data can be incomplete, noisy, or irregular, when I work with such data, I first perform a data cleaning process. I identify missing values, impute them using appropriate methods, or remove them from the analysis. I use filtering techniques to reduce noise. I also apply methods such as standardization and normalization to organize the data and make it analyzable.



## Chapter 2



```{r}
library(dslabs)
```{r}
data("polls_us_election_2016")


```{r}
# printing the first 10 rows of a dataset
knitr::kable(head(polls_us_election_2016, 10))



total_na <- sum(is.na(polls_us_election_2016))

# Display the total number of NA values
total_na

```


```{r}
polls_modified <- polls_us_election_2016

# Replace NA values in numeric columns with birth year and in character/factor columns with first name
polls_modified[] <- lapply(polls_modified, function(x) {
  if (is.numeric(x)) {
    x[is.na(x)] <- 1999  # Replace with your birth year
  } else if (is.character(x) || is.factor(x)) {
    x <- as.character(x)  # Convert factors to characters
    x[is.na(x)] <- "Muammer"  # Replace with your first name
  }
  return(x)
})

# Display the first 10 rows of the modified dataset
knitr::kable(head(polls_modified, 10))

```